Modeling vertical-axis cross-flow turbine wakes

### 2015-08-11 paper.tex
Both profiles are on one figure

Mean velocity profiles at one turbine diameter downstream are shown in
Figure~\ref{fig:mean-vel-profiles}. The 2-D results suffer from a blockage
mismatch, i.e. keeping the proximity of the walls constant increases the
blockage ratio.

\begin{figure}
\caption{Mean velocity profiles at $x/D=1$ from 2-D simulations, 3-D simulations
($z/H=0$), and experiments \cite{Bachant2015-JoT}.}
\label{fig:mean-vel-profiles}
\end{figure}

Turbulence kinetic energy profiles are shown in Figure~\ref{fig:k-profiles}. The
turbulence kinetic energy is calculated as
\begin{equation}
k = k_{\mathrm{RA}} + \frac{1}{2} \left( 
\overline{U^\prime}^2 + 
\overline{V^\prime}^2 + 
\overline{W^\prime}^2 \right),
\label{eq:k}
\end{equation}
where $U^\prime = U - \overline{U}$ and $k_{\mathrm{RA}}$ is the kinetic energy
calculated by the turbulence model, which is zero for the SA model. Note that
the statistics of the Reynolds-averaged velocity are calculated from a time
series that has been downsampled to 50 Hz. It is assumed that this is far enough
from the blade passage frequency that differences from the variance in the
original velocity will be negligible

\begin{figure}
\caption{Turbulence kinetic energy profiles at $x/D=1$ from 2-D simulations, 3-D
simulations ($z/H=0$), and experiments \cite{Bachant2015-JoT}.}
\label{fig:k-profiles}
\end{figure}

>>>>

Mean velocity profiles at one turbine diameter downstream are shown in
Figure~\ref{fig:profiles}. The 2-D results suffer from a blockage
mismatch, i.e. keeping the proximity of the walls constant increases the
blockage ratio.

\begin{figure}
\includegraphics[width=0.95\textwidth]{figures/profiles} \caption{Mean velocity
	(left) and turbulence kinetic energy (right) profiles at $x/D=1$ from 2-D
	simulations, 3-D simulations ($z/H=0$), and experiments \cite{Bachant2015-JoT}.}
\label{fig:profiles}
\end{figure}

Turbulence kinetic energy profiles are also shown in Figure~\ref{fig:profiles}.
The turbulence kinetic energy is calculated as
\begin{equation}
k = k_{\mathrm{RA}} + \frac{1}{2} \left( 
\overline{U^\prime}^2 + 
\overline{V^\prime}^2 + 
\overline{W^\prime}^2 \right),
\label{eq:k}
\end{equation}
where $U^\prime = U - \overline{U}$ and $k_{\mathrm{RA}}$ is the kinetic energy
calculated by the turbulence model, which is zero for the SA model. Note that
the statistics of the Reynolds-averaged velocity are calculated from a time
series that has been downsampled to 50 Hz. It is assumed that this is far enough
from the blade passage frequency that differences from the variance in the
original velocity will be negligible.
